Laws for Creating Trust in the Blockchain Age

### 2017-09-06 tex/article.tex
Added funding
Added co-authors
Added TradeChain explanation + image

  \author*[1]{Johan Pouwelse}
  \author[2]{Martijn de Vos}
  \runningauthor{Johan Pouwelse and Martijn de Vos}
  \affil[1]{Department of Software Technology, Delft University of Technology}
  \affil[2]{Department of Software Technology, Delft University of Technology}
  \title{Laws for Creating Trust in the Blockchain Age}
  \abstract{Humanity's notion of trust is shaped by new platforms operating in the emerging sharing economy, acting as intermediate matchmaker for ride sharing, housing facilities or freelance labour, effectively creating an environment where strangers trust each other. While millions of people worldwide rely on online sharing activities, such services are often facilitated by a few predatory companies, managing trust relations. This centralization of responsibility raises questions about ethical and political issues like regulatory compliance, data portability and monopolistic behaviour. Recently, blockchain technology has gathered a significant amount of support and adoption, due to its inherent decentralized and tamper-proof structure.\\We present a blockchain-powered blueprint for a shared and public \emph{programmable economy}. The focus of our architecture is on four essential primitives: digital identities, blockchain-based trust, programmable money and marketplaces. Trust is established using only historical interactions between strangers to estimate trustworthiness. Every component of our proposed technology stack is designed according to the defining principles of the Internet itself: self-governance, autonomy and shared ownership. Real-world viability of each component is demonstrated with a functional prototype or running code. Our vision is that the highlighted technology stack devises trust, new acts, principles and rules beyond the possibilities in current economic, legal and political systems.}
  \keywords{Blockchain, Trust, Programmable Economy, Transactions}

@@

@@

We created our decentralized marketplace and integrated it into Tribler.\footcite{pouwelse2008tribler}
The initial release of the marketplace supports trading bandwidth against both cyber- and regulated currencies, using the Internet-of-Money module discussed in Section \ref{sec:internet_of_money}.
Figure \ref{fig:tribler_market} shows the orderbook of a trader in the Tribler software.
Information about installed wallets of a trader are present in the upper-right corner of the window.

@@

>>>>

   %% Dutch Government Organisation for identity data
  % National Service for Identity Data, Netherlands
  %  Peter Hoogendoorn, ABN AMRO
  % Tim, Rotterdam Haven
  % Rikken, legal ?
  % CMS ?
  % Daimler
  % Chamber of Commerce, Netherlands

  \author*[1]{Johan Pouwelse}
  \author[2]{André de Kok}
  \author[3]{Joost Fleuren}
  \author[4]{Said Akdim}
  \author[5]{Peter Hoogendoorn}
  \author[6]{Martijn de Vos}
  \runningauthor{Johan Pouwelse and Martijn de Vos}
  \affil[1]{Department of Software Technology, Delft University of Technology}
  \affil[2]{National Service for Identity Data, Netherlands}
  \affil[3]{Chamber of Commerce, Netherlands}
  \affil[4]{Chamber of Commerce, Netherlands}
  \affil[5]{ABN AMRO}
  \affil[6]{Department of Software Technology, Delft University of Technology}
  %\affil[4]{Chamber of Commerce}
  \title{Laws for Creating Trust in the Blockchain Age}
  \abstract{Humanity's notion of trust is shaped by new platforms operating in the emerging sharing economy, acting as intermediate matchmaker for ride sharing, housing facilities or freelance labour, effectively creating an environment where strangers trust each other. While millions of people worldwide rely on online sharing activities, such services are often facilitated by a few predatory companies, managing trust relations. This centralization of responsibility raises questions about ethical and political issues like regulatory compliance, data portability and monopolistic behaviour. Recently, blockchain technology has gathered a significant amount of support and adoption, due to its inherent decentralized and tamper-proof structure.\\We present a blockchain-powered blueprint for a shared and public \emph{programmable economy}. The focus of our architecture is on four essential primitives: digital identities, blockchain-based trust, programmable money and marketplaces. Trust is established using only historical interactions between strangers to estimate trustworthiness. Every component of our proposed technology stack is designed according to the defining principles of the Internet itself: self-governance, autonomy and shared ownership. Real-world viability of each component is demonstrated with a functional prototype or running code. Our vision is that the highlighted technology stack devises trust, new acts, principles and rules beyond the possibilities in current economic, legal and political systems.}
  \keywords{Blockchain, Trust, Programmable Economy, Transactions}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=.9\columnwidth]{assets/tradechain}
	\caption{The TradeChain data structure, recording trades between two users.}
	\label{fig:tradechain}
\end{figure}

All transactions performed in the market are recorded on TradeChain, a data structure that is based on TrustChain (see Section \ref{sec:trustchain}).
The data structure is presented in Figure \ref{fig:tradechain}.
When a trader creates a new sell or buy offer, a new block is created, containing the order specification, and is signed by a random witness trader.
This witness validates the order and after signing, it sends the block to other traders.
When this offer has been matched against another offer, both traders publicly commit to the upcoming transaction: this is indicated by the \emph{tx\_init} block in Figure \ref{fig:tradechain}.
Next, the traders start exchanging assets.
For every exchange, a new block (named \emph{payment}) will be created, specifying the volume of assets that have been transferred during that specific payment.
Note that when both parties digitally sign this block, they agree that the assets have settled.
When all assets have been exchanged, a new block that completes the transaction is created and signed (named \emph{tx\_done}).

The structure displayed in Figure \ref{fig:tradechain} allows to detect disputes during transactions.
If a large amount of time has passed since a payment and the transaction has not been completed yet, it is possible to derive which trader should have transferred assets next.
This shows that TradeChain provides adequate evidence to resolve transaction disputes off-chain.

@@

We implemented our decentralized marketplace and integrated it into Tribler.\footcite{pouwelse2008tribler}
The initial release of the marketplace supports trading bandwidth against both cyber- and regulated currencies, using the Internet-of-Money module discussed in Section \ref{sec:internet_of_money}.
Figure \ref{fig:tribler_market} shows the orderbook of a trader in the Tribler software.
Information about installed wallets of a trader are present in the upper-right corner of the window.

@@

\funding{This work was funded by NWO/TKI grant 439.16.614.}
